Spá: a web-based viewer for text mining in Evidence Based Medicine

### 2014-04-24 documentation/paper.tex
s/*data is/*data are/ in paper

%Finding sentences or words with particular characteristics within a document is an important task in natural language processing and machine learning.
Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important and practical task in natural language processing and machine learning.
For example, \emph{systematic reviews} are fundamental tools in \ac{ebm} \cite{sackett1996}, and aim to answer clinical questions by exhaustively searching the literature for relevant studies.
During systematic reviewing data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases, is extracted and synthesized to produce a textual and statistical summary.
As an example, we demonstrate the task of bias assessment in which a reviewer assess, for example, whether the participants and personnel were properly blinded.
Assessing this is a time-consuming task, a single trial can take a domain expert around ten minutes \cite{Hartling2011}.
Making matters worse, a single review may typically include several dozen trials, and due to empirical low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus\cite{Hartling2009}.

>>>>

%Finding sentences or words with particular characteristics within a document is an important task in natural language processing and machine learning.
Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important and practical task in natural language processing and machine learning.
For example, \emph{systematic reviews} are fundamental tools in \ac{ebm} \cite{sackett1996}, and aim to answer clinical questions by exhaustively searching the literature for relevant studies.
During systematic reviewing data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases, are extracted and synthesized to produce a textual and statistical summary.
As an example, we demonstrate the task of bias assessment in which a reviewer assess, for example, whether the participants and personnel were properly blinded.
Assessing this is a time-consuming task, a single trial can take a domain expert around ten minutes \cite{Hartling2011}.
Making matters worse, a single review may typically include several dozen trials, and due to empirical low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus\cite{Hartling2009}.
